Report - Latest Rodent Data

### 2019-03-05 evaluation.Rmd
removing old top r chunks in rmds

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

@@

Here, we evaluate the models' abilities to hindcast the historic data.

>>>>

@@

Here, we evaluate the models' abilities to hindcast the historic data. This figure shows coverage (left column) and RMSE (right column) for each of a selection of historically common species and total rodents on the control (unmanipulated) plots only. The x-axis in each plot corresponds to the different models, including the ensemble. Each model's raw metric values are displayed for all included hindcasts (with jittering to show overlapping points) in addition to a summarizing quartile box-whisker (ends of the whiskers show the exteme values, box shows the 25%-75% range, horizontal line shows the median). The 90% coverage target is indicated by the horizontal dotted line.

```{r, hindcast_eval, echo=FALSE, fig.width=9, fig.height=15}
plot_cov_RMSE_mod_spp()
```

### 2019-03-05 report.Rmd
removing old top r chunks in rmds

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
'%>%' <- magrittr::'%>%'
source("tools/forecast_tools.R")
```

Here's the most recent actual data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE}
plot_cast_point(with_census = TRUE)
```

>>>>

Here's the most recent forecast for which observations have been made. The actual data (blue) are plotted in comparison to the forecast performed right before data collection (white, with error bars) for the control (unmanipulated) plots (top) and all plots together (bottom):
```{r, echo=FALSE}
plot_cast_point(with_census = TRUE)
```
